### 2022-06-02 main/chapter_2ljets.tex
add vrlow pre post fit

\subsection{Low}
\label{sec:2ljets_low}
Table~\ref{tab:2ljets_low}
Figure~\ref{fig:2ljets_low_region}
Figure~\ref{fig:2ljets_low2_region}
Figure~\ref{fig:2ljets_low_cr_region}
Figure~\ref{fig:2ljets_low_sr_or_cr_region}
Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt}
Figure~\ref{fig:2ljets_low_pre_post}
Figure~\ref{fig:2ljets_low_crz_extensions}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_EWKSR_Low_EWK_mjj_no_sr.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_EWKSR_Low_EWK_mjj.pdf}
\caption{}
\end{subfigure}
\caption[
Distribution of $\mjj$ in CR-Z and SR-Low with all systematic variations
]{%
Distribution of $\mjj$ in CR-Z and SR-Low with all systematic variations
(a) fitted to control regions, and (b) fitted to control and signal regions.
The arrows point in to the signal region, which shows a large peak in the
diboson background near $m(W)$.
Auxiliary materials to the paper~\cite{atlas2022searches} include (b), in which
the $\zjets$ background in SR-Low has been collapsed to fit the deficit.
Pre-fit yields are presented in Figures~\ref{fig:2ljets_low_sr_or_cr_region}
and~\ref{fig:2ljets_low_sr_or_cr_region_alt}.
}
\label{fig:2ljets_low_pre_post}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_met_EWK_met_Sign.pdf}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_met_EWK_met_Et.png}
\caption{}
\end{subfigure}
\caption[
Extension from CR-Z into higher (a) $\metsig$ and (b) $\met$
]{%
Extension from CR-Z into higher (a) $\metsig$ and (b) $\met$.
The arrow indicates the CR-Z  upper bound of $\metsig$; it has no hard
upper bound of $\met$.
Systematic uncertainties are extrapolated from CR-Z to the extended tail.
The tail overlaps with other regions, but shows good agreement with data.
Sub-figure (b) is reproduced from auxiliary material to the
paper~\cite{atlas2022searches}.
Each last bin includes overflow.
}
\label{fig:2ljets_low_crz_extensions}
\end{figure}

>>>>

\subsection{Low}
\label{sec:2ljets_low}
Table~\ref{tab:2ljets_low}
Figure~\ref{fig:2ljets_low_region}
Figure~\ref{fig:2ljets_low2_region}
Figure~\ref{fig:2ljets_low_cr_region}
Figure~\ref{fig:2ljets_low_sr_or_cr_region}
Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt}
Figure~\ref{fig:2ljets_low_crz_pre_post}
Figure~\ref{fig:2ljets_low_vrlow_pre_post}
Figure~\ref{fig:2ljets_low_crz_extensions}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_EWKSR_Low_EWK_mjj_no_sr.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_EWKSR_Low_EWK_mjj.pdf}
\caption{}
\end{subfigure}
\caption[
Distribution of $\mjj$ in CR-Z and SR-Low with all systematic variations
]{%
Distribution of $\mjj$ in CR-Z and SR-Low with all systematic variations
(a) fitted to control regions, and (b) fitted to control and signal regions.
The arrows point in to the signal region, which shows a large peak in the
diboson background near $m(W)$.
Auxiliary materials to the paper~\cite{atlas2022searches} include (b), in which
the $\zjets$ background in SR-Low has been collapsed to fit the deficit.
Pre-fit yields are presented in Figures~\ref{fig:2ljets_low_sr_or_cr_region}
and~\ref{fig:2ljets_low_sr_or_cr_region_alt}.
}
\label{fig:2ljets_low_crz_pre_post}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_prefit_VR_Low_EWK_met_Sign_no_sr.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_postfit_VR_Low_EWK_met_Sign.pdf}
\caption{}
\end{subfigure}
\caption[
Comparison of VR-Low before and after fitting to the signal regions
]{%
Comparison of VR-Low (a) before and (b) after fitting to the signal regions.
All systematic variations are included after fitting to the control regions.
The signal region deficit pulls the $\zjets$ below data in the validation
region, whose likelihood is not included in the \heplikelihood.
Figure (b) is reproduced from paper~\cite{atlas2022searches}.
Each last bin includes overflow.
}
\label{fig:2ljets_low_vrlow_pre_post}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_met_EWK_met_Sign.pdf}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_met_EWK_met_Et.png}
\caption{}
\end{subfigure}
\caption[
Extension from CR-Z into higher $\metsig$ and $\met$
]{%
Extension from CR-Z into higher (a) $\metsig$ and (b) $\met$.
The arrow indicates the CR-Z  upper bound of $\metsig$; it has no hard
upper bound of $\met$.
Systematic uncertainties are extrapolated from CR-Z to the extended tail.
The tail overlaps with other regions, but shows good agreement with data.
Sub-figure (b) is reproduced from auxiliary material to the
paper~\cite{atlas2022searches}.
Each last bin includes overflow.
}
\label{fig:2ljets_low_crz_extensions}
\end{figure}
